---
title: "Homework 4 Pettit Algorithm"
author: "Nathanael Roy"
date: "October 23, 2018"
output:
  html_document: default
  pdf_document: default
---
For our data we have 164 tests of a flight system, there were no failures in the first 137, then test 138 was a failure. There were no failures on tests 139 through 162, then 163 failed and 164 succeeded. We can encode this data as a series of ones and zeros:
```{r}
data = c(rep(0,137),1,rep(0,24),1,0)
```
Suppose we want to 


 Suppose we consider a statistic of the form 
 $$U_T = T S_t - tS_T$$
where $S_t = \sum_{i=1}^t x_i$

The Pettitt algorithm looks to identify a possible change point value by identifying the $argmin(U_T)$ for our sequence as well as every sequence with exactly the same number of 1s and 0s and then seeing where are value falls in the possible distribution of $U_T$ values. First, it would be good to have a general function to calculate $argmin(U_T)$ for our sequence. 

```{r}
#First we iterate from position 1 through T-1
Calc.U <- function(data){
  n = length(data)
  U.t = rep(0,n-1)
  for(i in 1:(n-1)){
    U.t[i] = n*sum(data[1:i]) - i*sum(data)
  }
  which(U.t==min(U.t))

  return(min(U.t))
}
U.t.data = Calc.U(data)
```


We then create all of the possible T choose m sequences of Xi that preserve $S_t = m$ and for each sequence calculate the U_t value.


```{r}
All.u = c()
for(i in 1:163){
  for(j in (i+1):164){
    new.data = rep(0,164)
    new.data[i] = 1
    new.data[j] = 1
    All.u = c(All.u,Calc.U(new.data))
  }
}
```
Using this new data point we can then plot a histogram of the possible values of U. A p value for our statistic is how extreme a value is compared to the other values of $U_t$ that are possible. We can calculate this value by dividing the number of values less than the value of our U by the total possible values of U.


```{r}
U.t.data
hist(All.u)
p = length(which(All.u < U.t.data))/length(All.u)
print(p)
```
Given our histogram and our p value we conclde that a change point happened. 

For the second part of our analysis we might ask what happens if the next 10 trials were successes, if our analysis would change?
```{r}
next.ten = c(rep(0,137),1,rep(0,24),1,0)


U.t.next.ten = Calc.U(data)

All.u.next.ten = c()
for(i in 1:173){
  for(j in (i+1):174){
    new.data = rep(0,174)
    new.data[i] = 1
    new.data[j] = 1
    All.u.next.ten = c(All.u.next.ten,Calc.U(new.data))
  }
}


U.t.next.ten
hist(All.u.next.ten)
p = length(which(All.u.next.ten < U.t.next.ten))/length(All.u.next.ten)
print(p)
```
This changes the analysis by a bit but it still seems likely that some sort of change has happened.






